A (sun)Shiny Recreation of the New York Times \n Weather Chart

### 2017-04-18 Paper.Rmd
fixed position on fig 3
Fixing figure 3, attempt 2

![Screenshot of Single Year Tab in Shiny App](Images/single_year_screenshot.png)

>>>>

```{r, fig.height = 3, fig.width = 12, warning = F, message = F, echo = F, fig.cap = "Screenshot of Single Year Tab in Shiny App"}
library(png)
library(grid)
img <- readPNG("Images/single_year_screenshot.png")
grid.raster(img)
```
